\documentclass[journal]{IEEEtran}

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{url}

\begin{document}

\title{Verification Appendix: Claim-to-Source Mapping for Lung Cancer Tree-Stack Manuscripts}
\author{Aryaman Anand}
\maketitle

\section{Purpose}
This appendix provides traceability for key claims and numeric statements in:
\begin{itemize}
    \item \texttt{Research\_Paper\_Draft\_IEEE.tex} (journal manuscript)
    \item \texttt{Research\_Paper\_Conference\_IEEE.tex} (conference manuscript)
\end{itemize}

No claim is marked as verified unless a concrete source is identified below.

\section{Project Artifact Sources}
\begin{itemize}
    \item \texttt{data/reports/mortality\_lightgbm\_nested\_cv.json}
    \item \texttt{data/reports/mortality\_xgboost\_nested\_cv.json}
    \item \texttt{data/reports/mortality\_tabnet\_nested\_cv.json}
    \item \texttt{data/reports/response\_lightgbm\_nested\_cv.json}
    \item \texttt{data/reports/response\_xgboost\_nested\_cv.json}
    \item \texttt{data/reports/response\_tabnet\_nested\_cv.json}
    \item \texttt{data/reports/data\_readiness\_report.json}
    \item \texttt{lungcancer/tree\_stack.py}
    \item \texttt{lungcancer/service.py}
\end{itemize}

\section{Literature Sources Used}
The following literature facts were sourced from user-provided summaries in chat, not independently fetched PDFs:
\begin{itemize}
    \item Zou et al. (JMIR Medical Informatics, 2025)
    \item Sun et al. (Frontiers in Oncology, 2024)
    \item Qureshi et al. (Scientific Reports, 2022)
    \item Li et al. (Genomics, Proteomics \& Bioinformatics, 2022)
\end{itemize}

\section{Claim-to-Source Table}
\renewcommand{\arraystretch}{1.08}
\begin{longtable}{p{0.28\textwidth}p{0.43\textwidth}p{0.23\textwidth}}
\toprule
\textbf{Claim} & \textbf{Value/Statement} & \textbf{Source} \\
\midrule
\endfirsthead
\toprule
\textbf{Claim} & \textbf{Value/Statement} & \textbf{Source} \\
\midrule
\endhead

Harmonized total rows & 585,148 & data\_readiness\_report.json \\
Mortality-ready rows & 552,781 & data\_readiness\_report.json \\
Response-ready rows & 901 & data\_readiness\_report.json \\
Source composition & SEER 580,328; cBio 3,754; GDC 1,066 & data\_readiness\_report.json \\

Mortality best model & LightGBM selected by AUC among 3 & mortality\_*.json \\
Mortality LightGBM AUC & outer\_mean AUC = 0.8114982015 & mortality\_lightgbm\_nested\_cv.json \\
Mortality LightGBM Brier & outer\_mean Brier = 0.1740118619 & mortality\_lightgbm\_nested\_cv.json \\
Mortality XGBoost AUC & outer\_mean AUC = 0.8105127751 & mortality\_xgboost\_nested\_cv.json \\
Mortality TabNet AUC & outer\_mean AUC = 0.7920986658 & mortality\_tabnet\_nested\_cv.json \\

Response best model & XGBoost selected by AUC among 3 & response\_*.json \\
Response XGBoost AUC & outer\_mean AUC = 0.9004346535 & response\_xgboost\_nested\_cv.json \\
Response XGBoost Brier & outer\_mean Brier = 0.1082890504 & response\_xgboost\_nested\_cv.json \\
Response LightGBM AUC & outer\_mean AUC = 0.8942783003 & response\_lightgbm\_nested\_cv.json \\
Response TabNet AUC & outer\_mean AUC = 0.7305759076 & response\_tabnet\_nested\_cv.json \\

AUC 95\% CI reporting & Present as \texttt{outer\_auc\_ci\_95} & all six nested\_cv reports \\
Threshold optimization & Present as \texttt{best\_threshold} with metrics & all six nested\_cv reports \\
Calibration metrics & Present with Brier and AUC & all six nested\_cv reports \\

Visualization artifacts & calibration, roc, probability hist for all models/tasks & all six nested\_cv artifact blocks \\
SHAP for tree models & SHAP artifacts for LightGBM/XGBoost; null for TabNet & nested\_cv artifact blocks \\

Auto-selection mechanism & Service ranks algorithm reports and loads best available & lungcancer/service.py \\
Training pipeline architecture & Nested CV + model-family branches + artifact writing & lungcancer/tree\_stack.py \\

Zou et al. mortality benchmark & C-index 0.702; 1y AUC 0.740; 3y 0.777; 5y 0.915 & user-provided summary \\
Sun et al. infection benchmark & LR test AUC 0.876; Brier 0.134 & user-provided summary \\
Qureshi et al. response benchmark & XGBoost accuracy 97.5\% in 4-class setting & user-provided summary \\
Li et al. review framing & ML landscape and modality integration challenges & user-provided summary \\

\bottomrule
\end{longtable}

\section{Unverified or Deferred Items}
\begin{itemize}
    \item No external PDF parsing was performed in this pass; literature values are from user-provided summaries.
    \item No new experiments were run during manuscript drafting; all project metrics come from existing report artifacts.
\end{itemize}

\section{Consistency Check Result}
The journal and conference manuscripts were drafted from the same numerical evidence base (project report JSON files listed above). Core model-ranking and metric statements are consistent across both documents.

\end{document}
